### 2020-12-19 Research Report - Boverhof/Tex report/main.tex

\section{Introduction} \label{Introduction}
The topic of mental workload has received widespread attention across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}.
A commonly utilized definition of mental workload, hereafter referred to as simply workload, is the demand placed upon humans whilst carrying out a certain task. As pointed out by de Waard (1996), such a definition is too shallow, for it defines workload solely in external sense. It is of importance to acknowledge that workload is person-specific construct, for the amount of experienced workload ushered by a given task may differ across people \cite{de1996measurement}. Hence, when referring to workload throughout this research, workload in its person-specific sense is meant.

A commonly employed method for assessing workload is the NASA-Task Load Index (or TLX) questionnaire, operationalizing workload in clusters of six different dimensions \cite{hart2006nasa}. Such measurements are usually conducted post experiment, which might be unpractical in certain situations. For example, consider an experiment with the objective of the assessing workload for pilots during a flight. Only well after the flight a measurement in the form of a questionnaire can occur, potentially generating bias. An example of such a bias is the observer bias, prescribing that actors participating in an experiment tend to over-exaggerate the treatment effect when having to report it themselves post-experiment \cite{mahtani2018catalogue}.

An alternative method for assessing workload is the measurement of bio-signals during the experiment, and use these to classify the degree workload. Examples of such bio-signals, hereafter referred to as modalities, include techniques such as electroencephalogram, eye tracking, galvanic skin response, functional near-infrared spectroscopy, etc. The advantage of this approach is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}. This yields an objective and rich multifaceted classification of a mental construct, such as workload. Additionally, a separate model for each individual can be trained, catering towards the personal perception of workload for that specific individual. This approach comes however at the cost of an increase in complexity, residing in the need to construct a complex framework that inputs the data from each of the utilized modalities, and ultimately outputs a single classification outcome.

The current research builds upon previous research conducted by \citeA{dolmans2020perceived}, who proposed a framework for multi-modular classification of workload with deep-learning. The current research differs from this previous endeavor in that it utilizes different modalities and data, but most importantly because it investigates the feasibility of a real-time approach. Real-time in this sense reflects the real-time classification of workload, that is classification whilst the experiment takes place. Doing so enables the possibility to alter the state of the experiment whilst it takes place, by responding towards the perceived workload of a participant. Such an approach may enable a wide range of possibilities: consider for example a flight simulation with the objective of educating pilots. Altering an experiment dynamically after the individual could substantially enhance the learning-experience, namely by anticipating on the perceived workload during a certain segment.

In order to build both frameworks, three modalities are included. These modalities include the techniques of electroencephalogram hereafter referred to as EEG, galvanic skin response hereafter referred to as GSR and photoplethysmography hereafter referred to as PPG. It is important to stress that the objective of the current research is not to gain insight into the most optimal model design for each of the previously delineated modalities. It is rather to construct a framework with which real-time classification can be managed, and to which modalities of choice can easily be added. Consequently, one of two design principles on which the architecture of the framework reclines is the principle of modularity. Modularity refers the extent to which different modalities can freely be added and/or removed towards the framework, without the necessity to re-architect and rebuild it entirely. The second adhered design principle is the principle generalizability, prescribing that the framework should not solely be utilizable in the context of workload, but also for the measurement of other mental constructs.

A deep-learning approach towards the construction of the real-time multi-modular framework is endeavored. Considering the complexity and sheer size of such a deep neural network, an important point of attention is speed. In order for real-time classification to be a possible, a swift and thus optimized network is required. The problem in real-	time classification with deep learning is often not the accuracy of classification, but rather the speed of classification. Deep neural networks easily involve thousands of calculations to be made simultaneously, which is even more true for a multi-modular approach as the current. In order for real-time classification to work, these calculations cannot take to long, for if they do the purpose of conducting a real-time approach in general renders redundant. The focus of the current research is therefore to architect and optimize a multi-modular deep neural network, which is capable of real-time classification, whilst still ensuring ample accuracy in classification. A total of four different network variations, each inhibiting a different degree of complexity, are assessed in their ability to classify in real-time, as well as their performance. Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, the state of which can be altered in real-time.

@@

\subsection{Related Work} \label{Relatedwork}
The current section will provide an overview of previous research on the network architecture for each modality separately. Additionally,  the most feasible architecture for the multi-modular framework in is entirety will be explored. In particular, attention is placed upon the data fusion, the real-time component and several model optimization techniques.

@@

\subsubsection{Second modality: Galvanic Skin Response (GSR)}
The second utilized modality is GSR, measuring sweat gland on the hands and hereby inferring arousal. GSR readings have been found to significantly increase as a consequence of an increase in task workload, hence constituting to be an objective predictor \cite{shi2007galvanic}.

@@

The previously delineated model as proposed by \citeA{biswas2019cornet} was adopted by \citeA{dolmans2020perceived}, and subsequently applied towards the MWL case. Batch normalisation and max pooling was performed in both contrasted networks \cite{dolmans2020perceived}.

\subsubsection{Fusion strategy}  
When architecting a multi-modular network, information streams stemming from different modalities are required to be combined, i.e. "fused", at one point in the network in order to ultimately result in a single classification. Fusion can be done at different locations, and in different ways. Several fusion strategies as proposed by \citeA{ramachandram2017deep} will be considered.

@@

Late, or decision level, fusion on the other hand refers to the process of aggregating the decisions from multiple models, each separately applied on each modalitiy separately. In case the data sources stemming from the various modalities are either correlated or inhibit a different dimensionality, late fusion is a much more feasible approach \cite{ramachandram2017deep}.

@@

\subsubsection{Experimental setup}
The experimental setting for data collection is the open-source spaceship video-game Empty Epsilon, in which the respondent is required to carry out tasks on a virtual spaceship \cite{daid2016empty}. This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab, hosted by the University of Twente (UT) and carried out in cooperation with Thales group Hengelo. The experiment constituted three different segments, during each of which the respondent had to carry out different tasks, all of which constructed to entail varying degrees of perceived workload. Each segment consists of six small sessions of roughly 5-10 minutes. These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment. A schematic overview of the experimental structure is delineated as table \ref{table:expsetup}. After each of the 18 sessions, respondents filled in the TLX questionnaire consisting of 6 questions each, resulting in 18 filled in questionnaires. Each questionnaire inquired upon the degree to which the respondent experienced workload during the previous session. These ratings have been use as labels in later training of the network. Within each segment, the order in which the sessions (varying in difficulty) were presented have been randomized. The order in which the segments were administrated were not random. Between every three sessions, respondents were requested to take a short 2 minute break.
\bigskip
\bgroup
\def\arraystretch{1.6}%  
\begin{table}[h]
\centering
\caption{Experimental setup: Number of sessions per segment and difficulty setting}
\label{table:expsetup}
\begin{tabular}{llll}
                               & Easy                   & Intermediate           & Hard                   \\ \cline{2-4} 
\multicolumn{1}{l|}{Segment 1} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
\multicolumn{1}{l|}{Segment 2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
\multicolumn{1}{l|}{Segment 3} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
\end{tabular}
\end{table}
\egroup
\bigskip

The first segment emulated a scenario in which hostile spaceships approach the respondent's spaceship. The respondent is required to  quickly react by defusing hostile spaceships in order to survive. The increment in difficulty caused the process of defusing hostile spaceships to be more challenging, and hereby to take longer,  aiming to increase workload as a consequence. The second segment emulated a scenario in which the respondent had to navigate their spaceship trough space, gathering as many way-points as possible. Obstacles around which the respondent had to carefully navigate were introduced in the intermediate difficult scenario, and hostile spaceships the respondent had to decimate were introduced in the hard scenario. Both increase difficulty, and hereby aim to increase workload as a consequence. The third and final segment emulated a machine room, in which respondents had to control the power based on randomly generated requests. Variables that could overheat the spaceship  were introduced as a consequence of an increase in difficulty, demanding the respondent to multi-task, hereby aiming to increase workload.

\subsubsection{Participants}
In total, twenty-five respondents are participating in the study. Currently, the data is still in the process of being collected, for which no additional descriptive statistics can be presented in the this section as of yet. The respondents are students, recruited from the University of Twente. Recruitment has been conducted with Sona, which is a cloud-based participant management system. Requirements were that respondents didn't have any constraints that might interfere with the utilized sensors, such as for example a pacemaker. This was assessed by means of a short demographic questionnaire prior to the experiment. Additionally, the respondents were made aware of ethical consent prior to the experiment, with the objective to ensure completely voluntary participation. Respondents were able to draw back from the experiment at any time.

@@

\subsubsection{Universal Framework Architecture}
The architecture for the proposed framework is constructed by combining insights from the literature, whilst keeping in mind the previously delineated design principles (i.e. the principles of modularity and generalizability). No variations based on the general framework architecture will be made, for deviating from the architectures as verified in the literature could be detrimental with regards to classification accuracy. A visual representation of the complete network is depicted as figure \ref{fig:architecture}.

\begin{figure}
\caption{Full Network Architecture}
\bigskip
\includegraphics[scale=0.725]{model_architecture}
\label{fig:architecture}
\end{figure}

@@

The networks for each of the modalities are finally closed with one fully connected dense layer, before feeding into the head network. This is done in order to flatten all inputs into a lower dimensional space, such that concatenation is possible. The head network consists of Four dense layers, alternated with some batch normalization and max-pooling layers, with the objective of stabilization.

\subsubsection{Model Variations}
Multi-modular classification in real-time by means of deep-learning requires an optimized network, as was elaborated upon in the introduction. Speed is a potential bottleneck, especially given the proposed network architecture is multi-modular, and substantially  complex. Different network variations will be investigated upon as a consequence of this. The aim is to propose a network that is fast enough for proper real-time classification, whilst ensuring the maximum amount of accuracy. Variations based on two different parameters of the network as depicted in figure \ref{fig:architecture} will therefore be considered, resulting in a total of four variations.

The first parameter constitutes the sampling rate for each of the included modalities. As was elaborated on earlier, data collection for each modality was conducted on a sampling rate of 256Hz. Naturally, an increase in classification speed can be attained by feeding less data into the network, i.e. decreasing the sampling rate. Two out of the four networks will consequently be fed data measured on a sampling rate of 256Hz, whilst the other two networks will input based on a sampling rate of 128Hz.

The second parameter reflects the amount of utilized filters for convolutional layers, and the amount of neurons for all utilized layers. A decrease in the amount of filters / neurons constitutes a decrease in network size, and consequently an increase in speed. Two out of the four models will be the full sized network, whilst the other two models will be halved in size. An overview of all four network variations is provided in table \ref{table:modelvariations}.

\bgroup
\def\arraystretch{1.6}%  
\begin{table}[h]
\centering
\caption{Model variation sizes}
\label{table:modelvariations}
\begin{tabular}{lllll}
\hline
                   & EEG        & GSR        & PPG        & Head       \\ \hline
Model 1: 128Hz \&  & Conv1: 25  & Conv1: 128 & Conv1: 128 & Dense: 712 \\
Model 2: 256Hz     & Conv2: 50  & Conv2: 128 & Conv2: 128 & Dense: 356 \\
                   & Conv3: 100 & LSTM1: 256 & LSTM1: 256 & Dense: 178 \\
                   & Conv4: 200 & LSTM1: 256 & LSTM2: 256 &            \\
                   \vspace{3ex}
                   & Dense: 200 & Dense: 256 & Dense: 256 &            \\ \hline
Model 3: 128 Hz \& & Conv1: 13  & Conv1: 64  & Conv1: 64  & Dense: 356 \\
Model 4: 256Hz     & Conv2: 25  & Conv2: 64  & Conv2: 64  & Dense: 178 \\
                   & Conv3: 50  & LSTM1: 128 & LSTM1: 128 & Dense: 89  \\
                   & Conv4: 100 & LSTM1: 128 & LSTM2: 128 &            \\
                   & Dense: 100 & Dense: 128 & Dense: 128 &            \\ \hline
\end{tabular}
\vspace{2ex}

>>>>

%Introduction section
\section{Introduction} \label{Introduction}
The topic of mental workload has received widespread attention across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}.
A commonly utilized definition of mental workload, hereafter referred to as simply workload, is the demand placed upon humans whilst carrying out a certain task. As pointed out by de Waard (1996), such a definition is too shallow, for it defines workload solely in external sense. It is of importance to acknowledge that workload is a person-specific construct, for the amount of experienced workload ushered by a given task may differ across people \cite{de1996measurement}. Hence, when referring to workload throughout this research, workload in its person-specific sense is meant.

A commonly employed method for assessing workload is the NASA-Task Load Index (or TLX) questionnaire, operationalizing workload in clusters of six different dimensions \cite{hart2006nasa}. Such an assessment is usually conducted post experiment, which in certain situations could be unpractical. For example, consider an experiment with the objective of the assessing workload for pilots during a flight. Only well after the flight a measurement in the form of a questionnaire can occur, potentially generating bias. An example of such a bias is the observer bias, prescribing that actors participating in an experiment tend to over-exaggerate the treatment effect, i.e. the degree if perceived workload, when having to report it themselves post-experiment \cite{mahtani2018catalogue}.

An alternative method for assessing workload is the measurement of bio-signals during the experiment, with which the degree workload is being classified. Examples of such bio-signals, hereafter referred to as modalities, include techniques such as electroencephalogram, eye tracking, galvanic skin response, functional near-infrared spectroscopy, etc. The advantage of this approach is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}. This yields an objective and rich multifaceted classification of a mental construct, such as workload. Additionally, a separate model for each individual can be trained, catering towards the personal perception of workload for that specific individual. This approach comes however at the cost of an increase in complexity, residing in the need to construct a complex framework that inputs the data from each of the utilized modalities, and ultimately outputs a single classification outcome.

The current research builds upon previous research conducted by \citeA{dolmans2020perceived}, who proposed a framework for multi-modular classification of workload with deep-learning. This research differs from this previous endeavor in that it utilizes different modalities and thus different data. However most importantly, the current research differs in that it investigates the feasibility of a real-time approach. Real-time in this sense considers the real-time classification of workload, that is classification whilst the experiment takes place. Doing so enables the possibility conduct a dynamic experiment, the state of which can be altered by responding towards the classified degree of workload for a participant. Consider a simulation with the objective of educating its participant, such as a flight simulator with the objective of educating trainee pilots. In such a situation, the ability to alter the state of the experiment dynamically, that is based on the amount of perceived workload, could substantially enhance the learning experience of a single session. Operations with which the trainee perceives high workload possibly require more practice, which could be dynamically integrated in the remainder of the experiment. Doing so has the potential of dramatically increasing the effectiveness of a single simulation session, hereby possibly entailing a more efficient learning process.

In order to build both frameworks, three modalities are included. These modalities include the techniques of electroencephalogram hereafter referred to as EEG, galvanic skin response hereafter referred to as GSR and photoplethysmography hereafter referred to as PPG. It is important to stress that the objective of the current research is not to gain insight into the most optimal model design for each of these previously delineated modalities. It is rather to construct a framework with which real-time classification can be managed, and to which modalities of choice can easily be added. Consequently, one of two design principles on which the architecture of the framework reclines is the principle of modularity. Modularity refers to the extent to which different modalities can freely be added and/or removed to the framework, without the necessity to re-architect and rebuild it entirely. The second adhered design principle is the principle of generalizability, prescribing that the framework should not solely be utilizable in the context of workload, but also for the measurement of other mental constructs.

A deep-learning approach towards the construction of the real-time multi-modular framework is endeavored. Considering the complexity and sheer size of such a network, an important point of attention is speed. In order for real-time classification to be possible, a swiftly classifying and hence optimized network is requisited. The challenge in real-time classification with deep-learning is often not reaching adequate performance, but rather to attain adequate speed of classification. Deep neural networks easily constitute thousands of calculations made simultaneously, which is even more so for a multi-modular approach. In order for real-time classification to work, classification cannot take too long, for if it does it is not real-time anymore. Firstly, for each of the three modalities a single-modular network is constructed and assessed in terms of speed and performance. Secondly, a multi-modular network is architected, and also assessed in terms of speed and performance. Additionally, several variations to this multi-modular framework are considered. These variations differ in their size, e.g. the amount of neurons and filters. The objective of the current research is to explore the circumstances in which a multi-modular approach by means of deep learning is capable of real-time classification, whilst still ensuring ample performance with respect to classification accuracy. Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, of which the state can be altered in real-time.

@@

\subsection{Related Work} \label{Relatedwork}
The current section will provide an overview of previous research on the most optimal network architecture for each modality separately. Additionally,  the most feasible architecture for the multi-modular framework in its entirety will be explored. In particular, attention is placed upon the data fusion strategy, the real-time component and several model optimization techniques.

@@

\subsubsection{Second modality: Galvanic Skin Response (GSR)}
The second utilized modality is GSR, measuring sweat gland on the hands and hereby inferring arousal. GSR activity have been found to significantly increase as a consequence of an increase in task workload, hence constituting to be an objective predictor \cite{shi2007galvanic}.

@@

\subsubsection{Fusion strategy}  
When architecting a multi-modular network, information streams stemming from different modalities are required to be combined, i.e. "fused", at one point in the network in order to ultimately result in a single classification. Fusion can be done at different locations, and in different ways. Several fusion strategies as proposed by \citeA{ramachandram2017deep} have been considered.

@@

Late, or decision level, fusion on the other hand refers to the process of aggregating the decisions from multiple models, each separately applied on each modalitiy separately. In case the data sources stemming from the various modalities are either correlated or ultimately inhibit a different dimensionality, late fusion is a much more feasible approach \cite{ramachandram2017deep}.

@@

\subsubsection{Experimental setup}
The experimental setting for data collection is the open-source spaceship video-game Empty Epsilon, in which the respondent is required to carry out tasks on a virtual spaceship \cite{daid2016empty}. This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab, hosted by the University of Twente and carried out in cooperation with Thales group Hengelo. The experiment constituted three different segments, during each of which the respondent had to carry out different tasks, all of which constructed to entail varying degrees of perceived workload. Each segment consists of six small sessions of roughly 5-10 minutes. These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment. A schematic overview of the experimental structure is delineated as table \ref{table:expsetup}. After each of the 18 sessions, respondents filled in the TLX questionnaire consisting of 6 questions each, resulting in 18 filled in questionnaires. Each questionnaire inquired upon the degree to which the respondent experienced workload during the previous session. These ratings have been use as labels in later training of the network. Within each segment, the order in which the sessions (varying in difficulty) were presented have been randomized. The order in which the segments were administrated were not random. Between every three sessions, respondents were requested to take a short 2 minute break.
\bigskip
\bgroup
\def\arraystretch{1.6}%  
\begin{table}[h]
\centering
\caption{Experimental setup: Number of sessions per segment and difficulty setting}
\label{table:expsetup}
\begin{tabular}{llll}
                               & Easy                   & Intermediate           & Hard                   \\ \cline{2-4} 
\multicolumn{1}{l|}{Segment 1} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
\multicolumn{1}{l|}{Segment 2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
\multicolumn{1}{l|}{Segment 3} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
\end{tabular}
\end{table}
\egroup
\bigskip

The first segment emulated a scenario in which hostile spaceships approach the respondent's spaceship. The respondent is required to  quickly react by defusing hostile spaceships in order to survive. The increment in difficulty caused the process of defusing hostile spaceships to be more challenging, and hereby to take longer,  aiming to increase workload as a consequence. The second segment emulated a scenario in which the respondent had to navigate their spaceship trough space, gathering as many way-points as possible. Obstacles around which the respondent had to carefully navigate were introduced in the intermediate difficult scenario, and hostile spaceships the respondent had to decimate were introduced in the hard scenario. Both increase difficulty, and hereby aim to increase workload as a consequence. The third and final segment emulated a machine room, in which respondents had to control the power based on randomly generated requests. Variables that could overheat the spaceship were introduced, demanding the respondent to multi-task, hence increasing difficulty.

\subsubsection{Participants}
In total, twenty-five respondents are participating in the study. Currently, the data is still in the process of being collected, for which no additional descriptive statistics can be presented in the this section as of yet. The respondents are students, recruited from the University of Twente. Recruitment has been conducted with Sona, which is a cloud-based participant management system. Requirements were that respondents didn't have any constraints that might interfere with the utilized sensors, such as for example a pacemaker. This was assessed by means of a short demographic questionnaire prior to the experiment. Additionally, the respondents were made aware of informed consent prior to the experiment, with the objective to ensure completely voluntary participation. Respondents were able to draw back from the experiment at any time.

@@

\subsubsection{Single-modular Network Architectures}
The architecture of each of the single-modular networks is determined by combining insights from the literature. Each network utilizes only a single modality. No variations from this network architecture will be made, for deviating from the architectures as verified in the literature could be detrimental with regards to performance. These separate networks are all depicted as figure \ref{fig:singlearchitecture}.

\begin{figure}
\caption{Three Single-modular Network Architectures}
\bigskip
\includegraphics[scale=0.725]{single_model_architecture}
\label{fig:singlearchitecture}
\end{figure}

@@

\subsubsection{Multi-modular Network Architecture}
The architecture for multi-modular approach is constructed by combining the single-modular networks as derived from the literature, whilst keeping in mind the previously delineated design principles (i.e. the principles of modularity and generalizability). A visual representation of the complete network is depicted as figure \ref{fig:multiarchitecture}.

\begin{figure}
\caption{Multi-modular Network Architecture}
\bigskip
\includegraphics[scale=0.725]{multi_model_architecture}
\label{fig:multiarchitecture}
\end{figure}

In order to combine the previously delineated single-modular networks, each of these distinct parts are closed with one fully connected dense layer before feeding into the head network. This is done in order to flatten all inputs into a lower dimensional space, such that concatenation is possible. The head network consists of Four dense layers, alternated with a batch normalization and max-pooling layers, with the objective of stabilization.

\subsubsection{Multi-modular Network Variations}
Multi-modular classification in real-time by means of deep-learning requires an optimized network, as was elaborated upon in the introduction. Speed is a potential bottleneck, especially given the proposed network architecture is multi-modular, and thus substantially complex. Consequently, different variations of the delineated network will be investigated upon. The aim is to propose a network that is fast enough for real-time classification, whilst ensuring the maximum amount of accuracy. Three different variations with regards to size of the network as depicted in figure \ref{fig:multiarchitecture} will therefore be considered.

Network size constitutes the amount of utilized filters for convolutional layers, and the amount of neurons for all other utilized layers. A decrease in the amount of filters and neurons constitutes a decrease in network size, and consequently a decrease in the amount of calculations. This is likely to bring about an increase in speed. An overview of all three multi-modular network variations, and the amount of utilized neurons/filters is provided in table \ref{table:modelvariations}. Network 1 is referred to as the full network, and is the biggest in terms of size. The size of network 2 constitutes of 75 \% of the size of the full network. Network 3 constitutes of 50 \% of the size of the full network.

\bgroup
\def\arraystretch{1.6}%  
\begin{table}[h]
\centering
\caption{Model variation sizes}
\label{table:modelvariations}
\begin{tabular}{lllll}
\hline
        & EEG        & GSR        & PPG        & Head       \\ \hline
Model 1 & Conv1: 25  & Conv1: 128 & Conv1: 128 & Dense: 712 \\
        & Conv2: 50  & Conv2: 128 & Conv2: 128 & Dense: 356 \\
        & Conv3: 100 & LSTM1: 256 & LSTM1: 256 & Dense: 178 \\
        & Conv4: 200 & LSTM1: 256 & LSTM2: 256 &            \\ 
        \vspace{3ex}
        & Dense: 200 & Dense: 256 & Dense: 256 &            \\ \hline
Model 2 & Conv1: 18  & Conv1: 96  & Conv1: 96  & Dense: 534 \\
        & Conv2: 34  & Conv2: 96  & Conv2: 96  & Dense: 267 \\
        & Conv3: 75  & LSTM1: 192 & LSTM1: 192 & Dense: 134 \\
        & Conv4: 150 & LSTM1: 192 & LSTM1: 192 &            \\
        \vspace{3ex}
        & Dense: 150 & Dense: 192 & Dense: 192 &            \\ \hline
Model 3 & Conv1: 13  & Conv1: 64  & Conv1: 64  & Dense: 356 \\
        & Conv2: 25  & Conv2: 64  & Conv2: 64  & Dense: 178 \\
        & Conv3: 50  & LSTM1: 128 & LSTM1: 128 & Dense: 89  \\
        & Conv4: 100 & LSTM1: 128 & LSTM2: 128 &            \\
        & Dense: 100 & Dense: 128 & Dense: 128 &            \\ \hline
\end{tabular}
\vspace{2ex}
